### 2021-03-04 paper3/appendix.tex
Fix headings and remove duplicate bib entries

\section{Appendix}\label{sec:zsf-appendix}
\subsection{Results for Adult Income}\label{sec:adult-results}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_partial_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with \emph{subgroup bias},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \textbf{l}abelled \textbf{d}eployment set; thus not suffering from bias in the training set.
    \textbf{Top left}: Accuracy.
    \textbf{Top right}: Positive rate ratio.
    \textbf{Bottom left}: True positive rate ratio.
    \textbf{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 69.7\% $\pm$ 0.3\%;
    for \texttt{K-means} it was 43\% $\pm$ 3\%.
    }%
    \label{fig:adult-subgroup-bias}
\end{figure*}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with a \emph{missing subgroup},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \textbf{l}abelled \textbf{d}eployment set; thus not suffering from bias in the training set.
    \textbf{Top left}: Accuracy.
    \textbf{Top right}: Positive rate ratio.
    \textbf{Bottom left}: True positive rate ratio.
    \textbf{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 60.4\% $\pm$ 0.8\%;
    for \texttt{K-means} it was 44\% $\pm$ 3\%.
    }%
    \label{fig:adult-missing-subgroup}
\end{figure*}
Figures~\ref{fig:adult-subgroup-bias} and \ref{fig:adult-missing-subgroup} show results from our method on the Adult Income dataset \cite{Dua:2017}.
This dataset is a common dataset for evaluating fair machine learning models. 
Each instance in the dataset is described by $14$ characteristics including gender, education, marital status, number of work hours per week among others, along with a label denoting income level ($\geq$\$50K or not). 
We transform the representation into $62$ real and binary features along with the subgroup label $s$. %%%%%%%%CHECK THESE VALUES%%%%%%%%%%%% 
The dataset is naturally imbalanced with respect to gender: 30\% of the males are labelled as earning more than \$50K per year (high income), while only 11\% of females are labelled as such.
For further details on the dataset construction, see section~\ref{ssec:dataset-construction-adult}.
%
Following standard practice in algorithmic fairness  e.g. \citet{ZemeWuSwePitetal13}, we consider gender to be the subgroup label $s$.

@@

\subsubsection{Coloured MNIST biasing parameters}
To simulate a real-word setting where the data, labelled or otherwise, is not naturally balanced, we bias the Coloured MNIST training and deployment sets by downsampling certain colour/digit combinations. The proportions of each such combination \emph{retained} in the \emph{subgroup bias} (in which we have one source missing from the training set) and \emph{missing subgroup} (in which we have two sources missing from the training set) are enumerated in table~\ref{color_mnist_biasing_po} and \ref{color_mnist_biasing_id}, respectively.
For the 3-digit-3-colour variant of the problem, no biasing is applied to either the deployment set or the training set (the missing combinations are specified in the caption accompanying figure~\ref{fig:cmnist-3dig-4miss-add}); this variant was experimented with only under the subgroup-bias setting.

@@

\subsubsection{Adult Income}\label{ssec:dataset-construction-adult}
For the Adult Income dataset, we do not need to apply any synthetic biasing as the dataset naturally contains some bias wrt $s$. Thus, we instantiate the deployment set as just a random subset of the original dataset. Explicit balancing of the test set is needed to yield meaningful evaluation, however, namely in the penalizing of biased classifiers, but need be taken in doing so. Balancing the test set such that
\begin{align}
    |\{x \in X |s=0, y=0\}| &= |\{x \in X |s=1, y=0\}|    \nonumber\\
    \text{and}~|\{x \in X |s=0, y=1\}| &= |\{x \in X |s=1, y=1\}|
\end{align}
where for both target classes, $y=0$ and $y=1$, the proportions of the groups $s=0$ and $s=1$ are made to be the same, is intuitive, yet at the same time precludes sensible comparison of the accuracy/fairness trade-off of the different classifiers.
Indeed, with the above conditions, a majority classifier (predicting all 1s or 0s) achieves comparable accuracy to the fairness-unaware baselines, while also yielding perfect fairness, by construction.
This observation motivated us to devise an alternative scheme, where we balance the test set according to the following constraints
\begin{align}
    & |\{x \in X |s=0, y=0\}| 
    = |\{x \in X |s=0, y=1\}|  \nonumber \\
    = &|\{x \in X |s=1, y=1\}|
    = |\{x \in X |s=1, y=0\}|~.
 \end{align}
That is, all subsets of $\gS \times \gY$ are made to be equally sized. Under this new scheme the accuracy of the the majority classifier is 50\% for the binary-classification task.

\subsection{Optimization}
\begin{table*}[p]
 \centering
 \caption{Selected hyperparameters for experiments with Coloured MNIST, Adult and CelebA datasets.}
 \label{tab:hparams}
 \begin{tabular}{llll}
 \toprule
 & \textbf{Coloured MNIST} & \textbf{Adult} & \textbf{CelebA}       
 \\ & 2-dig SB / 2-dig MS / 3-dig SB
 \\ \midrule
 Input size  &   $3 \times 32 \times 32$ & $61$ & $3 \times 64 \times 64$ \\  \midrule
 \multicolumn{4}{c}{Autoencoder}                     \\ \midrule
 Levels                      & $4$         & $1$    & $5$\\
 Level depth                 & $2$         & $1$    & $2$\\
 Hidden units / level        & $[32, 64, 128, 256]$ & $[61]$ & $[32, 64, 128, 256, 512]$\\
 Activation                  & GELU        & GELU   & GELU   \\
 Downsampling op.  & Strided Convs. & -- & Strided Convs.\\
 Reconstruction loss         & MSE         & Mixed$^1$  & MSE \\
 Learning rate               & $1 \times 10^{-3}$   & $1 \times 10^{-3}$  & $1 \times 10^{-3}$ \\ \midrule
 \multicolumn{4}{c}{Clustering}                      \\ \midrule
 Batch size                  & $256$      & $1000$  & --\\
 AE pre-training epochs      & $150$        & $100$ & --   \\
 Clustering epochs           & $100$       & $300$  & -- \\
 Self-supervised loss & Cosine + BCE & Cosine + BCE & --\\
 U (for ranking statistics)             & $5$         & $3$     & --    \\   \midrule
 \multicolumn{4}{c}{Distribution Matching}                   \\ \midrule
 Batch size & $1$/$32$/$14$  & $64$   & $32$ \\
 Bag size   & $256$/$8$/$18$ & $32$ & $8$ \\
 Training iterations    & $8\text{k}/8\text{k}/20\text{k}$ & $5\text{k}$ & $15\text{k}$ \\
 Encoding ($z$) size$^2$  & $128$   & $35$  & $128$ \\
 Binarised $z_s$ & {\boxedsymbols ✗}\, / \cmark\, / \cmark & \xmark & \xmark \\
 $y$-predictor weight ($\lambda_1$) & $1$ & $0$ & $1$  \\ 
 $s$-predictor weight ($\lambda_2$) & $1$ & $0$ & $0$  \\ 
 Adversarial weight ($\lambda_3$)   & $1 \times
 10^{-3}$   & $1$   & $1$\\ 
 Stopgradient $\left(\nabla_\theta h_\psi(f_\theta(X^\mathit{dep}))=0\right)$ & \xmark & \cmark & \xmark \\
 \midrule
 \multicolumn{4}{c}{Predictors}   \\ \midrule
 Learning rate  & $3 \times 10^{-4}$ &   $1 \times 10^{-3}$  $ 1 \times 10^{-3}$\\
 \midrule
 \multicolumn{4}{c}{Discriminator}                   \\ \midrule
 Attention mechanism$^3$    & Gated   & Gated & Gated \\
 Hidden units pre-aggregation  & $[256, 256]$  & $[32]$ & $[256, 256]$\\
 Hidden units post-aggregation & $[256, 256]$ & --  & $[256, 256]$ \\
 Embedding dim (for attention) & $32$ & $128$ & $128$ \\
 Activation & GELU & GELU & GELU \\
 Learning rate  & $3 \times 10^{-4}$    & $1 \times 10^{-3}$ & $1 \times 10^{-3}$\\
 Updates / AE update    & $1$  & $3$    & $1$    \\
 \bottomrule
 \multicolumn{4}{l}{\footnotesize $^1$ Cross-entropy is used for categorical features, MSE for continuous features.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^2$ $|z|$ denotes the combined size of $z_s$ and $z_y$, with the former occupying $\ceil{\text{log}_2(\mathcal{S})}$ dimensions, the latter the remaining } \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize dimensions.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^3$ The attention mechanism used for computing the sample-weights within a bag. \emph{Gated} refers to gated attention  proposed by
%   \cite{ilse2018attention}, while \emph{SDP} refers to the scaled dot-product attention proposed by \cite{vaswani2017attention}.
  } \\ 
  \multicolumn{4}{p{\textwidth}}{\footnotesize  \cite{ilse2018attention}.} \\ 
 \end{tabular}
\end{table*}

The hyperparameters and architectures for the Autoencoder (\texttt{AE}), Predictor and Discriminator subnetworks used for the experiments with all datasets are detailed in Table \ref{tab:hparams}. All networks are trained using the Adam optimiser \citep{KinBa15}.

@@

For the \texttt{DRO} baseline, we allowed access to the labels of the test set for the purpose of hyperparameters selection, performing a grid-search over multiple splits to avoid overfitting to any particular instantiation.
Specifically, the threshold ($\eta$) parameter for \texttt{DRO} was determined by a grid-search over the space $\{0.01, 0.1, 0.3, 1.0\}$. The same procedure was carried out for selecting the model capacity constant ( $C$) of the related \texttt{gDRO} baseline.

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/celeba_attn_map.png}
    % \end{subfigure}
    % \hfill
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{figures/cmnist_attn_map.png}
    % \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Colored MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}

@@

\subsection{Code}
A \texttt{.zip} file is included containing all files needed to reproduce our experiments. Instructions on how to run them can be found in the \texttt{README.md}.

@@

  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_overcluster_acc.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_overcluster_prr.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_overcluster_tprr.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_overcluster_tnrr.pdf}

@@

    Results from \textbf{30 repeats} for the Coloured MNIST dataset with two digits, 2 and 4, with \emph{subgroup bias} for the colour `{\color{purple}purple}': for {\color{purple}purple}, only the digit class `2' is present.
    \textbf{Top left}: Accuracy.
    \textbf{Top right}: Positive rate ratio.
    \textbf{Bottom left}: True positive rate ratio.
    \textbf{Bottom right}: True negative rate ratio.

@@

  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_acc.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_prr.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tprr.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tnrr.pdf}

@@

    Results from \textbf{30 repeats} for the Coloured MNIST dataset with two digits, 2 and 4, with a \emph{missing subgroup}: the training dataset only has {\color{green}green} digits.
    \textbf{Top left}: Accuracy.
    \textbf{Top right}: Positive rate ratio.
    \textbf{Bottom left}: True positive rate ratio.
    \textbf{Bottom right}: True negative rate ratio.

@@

  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_prr-min.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_prd-max.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_tprr-min.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_tprd-max.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_tnrr-min.pdf}
  \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_tnrd-max.pdf}

@@

    Results from \textbf{30 repeats} for the Coloured MNIST dataset with three digits: `2', `4' and `6'.

@@

    % \textbf{First row}: Hirschfeld-Gebelein-R\'enyi maximal correlation between $S$ and $Y$.
    \textbf{First row, left}: minimum of all positive rate ratios.
    \textbf{First row, right}: maximum of all positive rate differences.
    \textbf{Second row, left}: minimum of all true positive rate ratios.
    \textbf{Second row, right}: maximum of all true positive rate differences.
    \textbf{Third row, left}: minimum of all true negative rate ratios.
    \textbf{Third row, right}: maximum of all true negative rate differences.

@@

    Results from \textbf{10 repeats} for the CelebA dataset with the \emph{subgroup bias} setting.

@@

    % \textbf{Top left}: Accuracy.
    % \textbf{Top right}: Positive rate ratio.
    \textbf{Left}: True positive rate ratio.
    \textbf{Right}: True negative rate ratio.

>>>>

\section{Appendix}\label{sec:zsf-appendix}
\subsection{Results for Adult Income}\label{sec:adult-results}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_partial_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with \emph{subgroup bias},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 69.7\% $\pm$ 0.3\%;
    for \texttt{K-means} it was 43\% $\pm$ 3\%.
    }%
    \label{fig:adult-subgroup-bias}
\end{figure*}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with a \emph{missing subgroup},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 60.4\% $\pm$ 0.8\%;
    for \texttt{K-means} it was 44\% $\pm$ 3\%.
    }%
    \label{fig:adult-missing-subgroup}
\end{figure*}
Figures~\ref{fig:adult-subgroup-bias} and \ref{fig:adult-missing-subgroup} show results from our method on the Adult Income dataset \cite{Dua:2017}.
This dataset is a common dataset for evaluating fair machine learning models. 
Each instance in the dataset is described by $14$ characteristics including gender, education, marital status, number of work hours per week among others, along with a label denoting income level ($\geq$\$50K or not). 
We transform the representation into $62$ real and binary features along with the subgroup label $s$. %%%%%%%%CHECK THESE VALUES%%%%%%%%%%%% 
The dataset is naturally imbalanced with respect to gender: 30\% of the males are labelled as earning more than \$50K per year (high income), while only 11\% of females are labelled as such.
For further details on the dataset construction, see section~\ref{ssec:dataset-construction-adult}.
%
Following standard practice in algorithmic fairness, e.g. \citet{zemel2013learning}, we consider gender to be the subgroup label $s$.

@@

\paragraph{Coloured MNIST biasing parameters.}
To simulate a real-word setting where the data, labelled or otherwise, is not naturally balanced, we bias the Coloured MNIST training and deployment sets by downsampling certain colour/digit combinations. The proportions of each such combination \emph{retained} in the \emph{subgroup bias} (in which we have one source missing from the training set) and \emph{missing subgroup} (in which we have two sources missing from the training set) are enumerated in table~\ref{color_mnist_biasing_po} and \ref{color_mnist_biasing_id}, respectively.
For the 3-digit-3-colour variant of the problem, no biasing is applied to either the deployment set or the training set (the missing combinations are specified in the caption accompanying figure~\ref{fig:cmnist-3dig-4miss-add}); this variant was experimented with only under the subgroup-bias setting.

@@

\paragraph{Adult Income.}\label{ssec:dataset-construction-adult}
For the Adult Income dataset, we do not need to apply any synthetic biasing as the dataset naturally contains some bias wrt $s$. Thus, we instantiate the deployment set as just a random subset of the original dataset. Explicit balancing of the test set is needed to yield meaningful evaluation, however, namely in the penalizing of biased classifiers, but need be taken in doing so. Balancing the test set such that
\begin{align}
    |\{x \in X |s=0, y=0\}| &= |\{x \in X |s=1, y=0\}|    \nonumber\\
    \text{and}~|\{x \in X |s=0, y=1\}| &= |\{x \in X |s=1, y=1\}|
\end{align}
where for both target classes, $y=0$ and $y=1$, the proportions of the groups $s=0$ and $s=1$ are made to be the same, is intuitive, yet at the same time precludes sensible comparison of the accuracy/fairness trade-off of the different classifiers.
Indeed, with the above conditions, a majority classifier (predicting all 1s or 0s) achieves comparable accuracy to the fairness-unaware baselines, while also yielding perfect fairness, by construction.
This observation motivated us to devise an alternative scheme, where we balance the test set according to the following constraints
\begin{align}
    & |\{x \in X |s=0, y=0\}| 
    = |\{x \in X |s=0, y=1\}|  \nonumber \\
    = &|\{x \in X |s=1, y=1\}|
    = |\{x \in X |s=1, y=0\}|~.
 \end{align}
That is, all subsets of $\gS \times \gY$ are made to be equally sized. Under this new scheme the accuracy of the the majority classifier is 50\% for the binary-classification task.

\subsection{Optimization}
\begin{table*}[p]
 \centering
 \caption{Selected hyperparameters for experiments with Coloured MNIST, Adult and CelebA datasets.}
 \label{tab:hparams}
\scalebox{0.65}{
 \begin{tabular}{llll}
 \toprule
 & \textsc{Coloured MNIST} & \textsc{Adult} & \textsc{CelebA}       
 \\ & 2-dig SB / 2-dig MS / 3-dig SB
 \\ \midrule
 Input size  &   $3 \times 32 \times 32$ & $61$ & $3 \times 64 \times 64$ \\  \midrule
 \multicolumn{4}{c}{Autoencoder}                     \\ \midrule
 Levels                      & $4$         & $1$    & $5$\\
 Level depth                 & $2$         & $1$    & $2$\\
 Hidden units / level        & $[32, 64, 128, 256]$ & $[61]$ & $[32, 64, 128, 256, 512]$\\
 Activation                  & GELU        & GELU   & GELU   \\
 Downsampling op.  & Strided Convs. & -- & Strided Convs.\\
 Reconstruction loss         & MSE         & Mixed$^1$  & MSE \\
 Learning rate               & $1 \times 10^{-3}$   & $1 \times 10^{-3}$  & $1 \times 10^{-3}$ \\ \midrule
 \multicolumn{4}{c}{Clustering}                      \\ \midrule
 Batch size                  & $256$      & $1000$  & --\\
 AE pre-training epochs      & $150$        & $100$ & --   \\
 Clustering epochs           & $100$       & $300$  & -- \\
 Self-supervised loss & Cosine + BCE & Cosine + BCE & --\\
 U (for ranking statistics)             & $5$         & $3$     & --    \\   \midrule
 \multicolumn{4}{c}{Distribution Matching}                   \\ \midrule
 Batch size & $1$/$32$/$14$  & $64$   & $32$ \\
 Bag size   & $256$/$8$/$18$ & $32$ & $8$ \\
 Training iterations    & $8\text{k}/8\text{k}/20\text{k}$ & $5\text{k}$ & $15\text{k}$ \\
 Encoding ($z$) size$^2$  & $128$   & $35$  & $128$ \\
 Binarised $z_s$ & {\boxedsymbols ✗}\, / \cmark\, / \cmark & \xmark & \xmark \\
 $y$-predictor weight ($\lambda_1$) & $1$ & $0$ & $1$  \\ 
 $s$-predictor weight ($\lambda_2$) & $1$ & $0$ & $0$  \\ 
 Adversarial weight ($\lambda_3$)   & $1 \times
 10^{-3}$   & $1$   & $1$\\ 
 Stopgradient $\left(\nabla_\theta h_\psi(f_\theta(X^\mathit{dep}))=0\right)$ & \xmark & \cmark & \xmark \\
 \midrule
 \multicolumn{4}{c}{Predictors}   \\ \midrule
 Learning rate  & $3 \times 10^{-4}$ &   $1 \times 10^{-3}$  $ 1 \times 10^{-3}$\\
 \midrule
 \multicolumn{4}{c}{Discriminator}                   \\ \midrule
 Attention mechanism$^3$    & Gated   & Gated & Gated \\
 Hidden units pre-aggregation  & $[256, 256]$  & $[32]$ & $[256, 256]$\\
 Hidden units post-aggregation & $[256, 256]$ & --  & $[256, 256]$ \\
 Embedding dim (for attention) & $32$ & $128$ & $128$ \\
 Activation & GELU & GELU & GELU \\
 Learning rate  & $3 \times 10^{-4}$    & $1 \times 10^{-3}$ & $1 \times 10^{-3}$\\
 Updates / AE update    & $1$  & $3$    & $1$    \\
 \bottomrule
 \multicolumn{4}{l}{\footnotesize $^1$ Cross-entropy is used for categorical features, MSE for continuous features.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^2$ $|z|$ denotes the combined size of $z_s$ and $z_y$, with the former occupying $\ceil{\text{log}_2(\mathcal{S})}$ dimensions, the latter the remaining } \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize dimensions.} \\
  \multicolumn{4}{p{\textwidth}}{\footnotesize $^3$ The attention mechanism used for computing the sample-weights within a bag. \emph{Gated} refers to gated attention  proposed by
%   \cite{ilse2018attention}, while \emph{SDP} refers to the scaled dot-product attention proposed by \cite{vaswani2017attention}.
  } \\ 
  \multicolumn{4}{p{\textwidth}}{\footnotesize  \cite{ilse2018attention}.} \\ 
 \end{tabular}
}
\end{table*}

The hyperparameters and architectures for the Autoencoder (\texttt{AE}), Predictor and Discriminator subnetworks used for the experiments with all datasets are detailed in Table \ref{tab:hparams}. All networks are trained using the Adam optimiser \citep{kingma2015adam}.

@@

For the \texttt{DRO} baseline, we allowed access to the labels of the test set for the purpose of hyperparameters selection, performing a grid-search over multiple splits to avoid overfitting to any particular instantiation.
Specifically, the threshold ($\eta$) parameter for \texttt{DRO} was determined by a grid-search over the space $\{0.01, 0.1, 0.3, 1.0\}$. The same procedure was carried out for selecting the model capacity constant ($C$) of the related \texttt{gDRO} baseline.

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{figures/celeba_attn_map.png}
    % \end{subfigure}
    % \hfill
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{figures/cmnist_attn_map.png}
    % \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Colored MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}

@@

\subsection{Code}
The code will be published at the following URL: \url{https://github.com/predictive-analytics-lab/fair-dist-matching}.
Instructions on how to run them can be found in the \texttt{README.md}.

@@

  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_tnrr.pdf}

@@

    Results from 30 repeats for the Coloured MNIST dataset with two digits, 2 and 4, with \emph{subgroup bias} for the colour `{\color{purple}purple}': for {\color{purple}purple}, only the digit class `2' is present.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.

@@

  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tnrr.pdf}

@@

    Results from 30 repeats for the Coloured MNIST dataset with two digits, 2 and 4, with a \emph{missing subgroup}: the training dataset only has {\color{green}green} digits.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.

@@

  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_prr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_prd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tprr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tprd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tnrr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tnrd-max.pdf}

@@

    Results from 30 repeats for the Coloured MNIST dataset with three digits: `2', `4' and `6'.

@@

    % \textsc{First row}: Hirschfeld-Gebelein-R\'enyi maximal correlation between $S$ and $Y$.
    \textsc{First row, left}: minimum of all positive rate ratios.
    \textsc{First row, right}: maximum of all positive rate differences.
    \textsc{Second row, left}: minimum of all true positive rate ratios.
    \textsc{Second row, right}: maximum of all true positive rate differences.
    \textsc{Third row, left}: minimum of all true negative rate ratios.
    \textsc{Third row, right}: maximum of all true negative rate differences.

@@

    Results from 10 repeats for the CelebA dataset with the \emph{subgroup bias} setting.

@@

    % \textsc{Top left}: Accuracy.
    % \textsc{Top right}: Positive rate ratio.
    \textsc{Left}: True positive rate ratio.
    \textsc{Right}: True negative rate ratio.
